\resumeSubHeadingListStart

    % Projet 1 : Kaggle (Impact & Visibilité)
    \resumeSubheading
      {Mastocytosis Patient Survey – Data Analysis \& Visualization}{Personal Project}
      {Kaggle Platform}{Jan. 2025 -- Feb. 2025}
      \resumeItemListStart
        \resumeItem{Performed exploratory data analysis (EDA) on a healthcare dataset to identify trends in patient symptoms and treatments.}
        \resumeItem{Achieved significant community impact with over \textbf{1,200 views} and \textbf{117 downloads} on the Kaggle platform.}
        \resumeItem{Developed interactive visualizations to communicate complex medical findings to a non-technical audience.}
      \resumeItemListEnd

    % Projet 2 : LEGO API (Dev & Data Engineering)
    \resumeSubheading
      {Lego Sets Collector – API Integration \& Web Generation}{BUT SD}
      {Academic Group Project}{Nov. 2025 -- Dec. 2025}
      \resumeItemListStart
        \resumeItem{Built a Python-based terminal application to harvest real-time data from the \textbf{Brickset API}.}
        \resumeItem{Engineered a feature to automatically generate custom HTML reports, allowing users to filter and visualize sets by release year.}
        \resumeItem{Awarded the \textbf{highest grade in the cohort} for technical execution and code architecture.}
        \resumeItem{Collaborated with 2 peers using Git for version control and efficient workflow management.}
      \resumeItemListEnd

    % Projet 3 : Séries Temporelles (Statistiques avancées)
    \resumeSubheading
      {Time Series Forecasting: Housing Rental Turnover Index}{BUT SD}
      {Academic Statistical Report}{Sep. 2025 -- Nov. 2025}
      \resumeItemListStart
        \resumeItem{Conducted a comprehensive 15-page study on French housing rental data (2010–2015) using \textbf{R} for data processing and statistical analysis.}
        \resumeItem{Implemented \textbf{Holt-Winters exponential smoothing} and linear trend modeling using R packages to generate short-term forecasts.}
        \resumeItem{Developed advanced data visualizations with \textbf{ggplot2} to communicate seasonal patterns and trend decompositions.}
        \resumeItem{Validated models through rigorous residual analysis and performance comparison (MSE/MAE metrics).}
      \resumeItemListEnd

\resumeSubHeadingListEnd