\section{Work Experience}
  \resumeSubHeadingListStart

    % 1. Hager Group - Software focus
    \resumeSubheading
      {Hager Group}{Obernai, France}
      {Apprentice Software Engineer}{Sep. 2023 -- Aug. 2024}
      \resumeItemListStart
        \resumeItem{Designed and implemented Power BI dashboards to monitor key business activities, improving data visibility for the international team.}
        \resumeItem{Led data analysis for the "Waldo Desk" project, ensuring the integration and maintenance of the Flex Office system for over 300 users.}
        \resumeItem{Developed automated PowerShell scripts to streamline team workflows, reducing manual processing time by 30\%.}
        \resumeItem{Provided statistical reports and insights to optimize office space utilization, supporting management in data-driven decision-making.}
        \resumeItem{Collaborated effectively within an international Agile team, ensuring seamless delivery of digital solutions in a Git environment.}
      \resumeItemListEnd
    
    % 2. Hager Group - Support
    \resumeSubheading
      {Hager Group}{Obernai, France}
      {Apprentice Service Desk Analyst}{Aug. 2022 -- Aug. 2023}
      \resumeItemListStart
        \resumeItem{Resolved hardware and network issues for internal clients, maintaining a high satisfaction rate through professional remote and on-site assistance.}
        \resumeItem{Managed incident tracking and reporting, working autonomously to prioritize and resolve over 200 tickets per month.}
      \resumeItemListEnd

    % 3. Microstars - Minimisé
    \resumeSubheading
      {Microstars}{Strasbourg, France}
      {Apprentice IT Technician}{Oct. 2020 -- Aug. 2022}
      \resumeItemListStart
        \resumeItem{Performed hardware installations and technical documentation for professional clients.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd